Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-12 paper.tex
Rephrase

We believe that there is also a broader take-away for an audience of
stubbornly French functional programmers. The present work surfs on
the wake of the Squiggol school of
programming~\citep{bird:squiggol,roconnor:functor-oriented}. Because our
government-approved programming language does not yet support ad-hoc
polymorphism~\citep{white:modular-implicit}, the French community may be
missing out on some interesting programming patterns. The present
article can thus be read as a case-study in ``functor-oriented
programming'', where the word ``functor'' is taken in his categorical
meaning (recalled in Section~\ref{sec:spec} and unrelated to the one
mentioned in the ML module system). In effect, we forbid ourselves
from programming over a concrete datastructure: instead, we rely on
(categorical) functors, peppered with some more structure, so as to 1.
unlock algebraic manipulation during compilation and 2. exploit
parametricity for reasoning.

>>>>

We believe that there is also a broader take-away for an audience of
stubbornly French functional programmers. The present work surfs on
the wake of the Squiggol school of programming~\citep{bird:squiggol}.
Because our government-approved programming language does not yet
support ad-hoc polymorphism~\citep{white:modular-implicit}, the French
community may be missing out on some interesting programming patterns.
The present article can thus be read as a case-study in
``functor-oriented programming''~\citep{roconnor:functor-oriented},
where the notion of functor comes from category theory (recalled in
Section~\ref{sec:spec} and unrelated to the notion used in ML module
systems). In effect, we forbid ourselves from programming over a
concrete datastructure: instead, we rely on (categorical) functors,
peppered with some more structure, so as to 1. unlock algebraic
manipulation during compilation and 2. exploit parametricity for
reasoning.
